---
title: 'Initial Exploratory Data Analysis On Video Game Sales'
author: "Ahmet Tuncel"
date: "22 Ekim 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
This dataset contains a list of video games with sales greater than 100,000 copies. It was generated by a scrape of vgchartz.com.


Fields include

1. Rank - Ranking of overall sales
2. Name - The games name
3. Platform - Platform of the games release (i.e. PC,PS4, etc.)
4. Year - Year of the game's release
5. Genre - Genre of the game
6. Publisher - Publisher of the game
7. NA_Sales - Sales in North America (in millions)
8. EU_Sales - Sales in Europe (in millions)
9. JP_Sales - Sales in Japan (in millions)
10. Other_Sales - Sales in the rest of the world (in millions)
11. Global_Sales - Total worldwide sales.
12. The script to scrape the data is available at https://github.com/GregorUT/vgchartzScrape. It is based on 
13. BeautifulSoup using Python. There are 16,598 records. 2 records were dropped due to incomplete information.

```{r Video Game Sales}

data = read.csv("vgsales.csv", header = TRUE)
str(data)

```

## Data Visualizations

1. Sales In Data Platform:

```{r Sales Data Platform, echo=FALSE, message=FALSE, warning=FALSE}
library(shiny)
library(plotly)

data = read.csv("vgsales.csv", header = TRUE)


plot_ly(y=data$EU,x=data$Year,mode = 'lines',name='Europe Sale')%>%
  add_trace(y=data$AME,x=data$Year,name='American Sale',mode = 'lines')%>%
  add_trace(y=data$Global,x=data$Year,name='Global Sale',mode = 'lines')%>%
  add_trace(y=data$JP,x=data$Year,name='Japen Sales',mode = 'lines')%>%
  add_trace(y=data$Other,x=data$Year,name='Other Regions',mode = 'lines')%>%
  layout(title = "Sales in data Platform",
         scene = list(
           xaxis = list(title = "Year"), 
           yaxis = list(title = "Sales")))





```









2. Genre Popularity over the Years:

```{r Genre Popularity over Years, echo=FALSE, message=FALSE, warning=FALSE}



data %>% 
  ggplot(aes(x = Year, y = Global_Sales, fill = Genre)) +
  geom_bar(stat = "identity") +
  labs(title = "Genre Popularity over Years", x = "Year", y = "Global Sales (in milion copies)") +
  scale_x_discrete(breaks = as.character(seq(from = 1980, to = 2016, by = 4))) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_fill_brewer(palette = "Set3")
```

